1) Shan H. Siddiqi, M.D., Department of Psychiatry, Washington University School of Medicine, St. Louis, Missouri, USA.

2) Natalia K. Abraham, M.D., School of Epidemiology, Public Health and Preventive Medicine, University of Ottawa, Ottawa, Ontario, Canada.

3) Christopher L. Geiger, M.D., Department of Internal Medicine, University of Washington, Seattle, Washington, USA.

4) Morvarid Karimi, M.D., Department of Neurology, Washington University School of Medicine, St. Louis, Missouri, USA.

5) Joel S. Perlmutter, M.D., Departments of Neurology, Radiology, and Anatomy & Neurobiology, Division of Biology and Biomedical Sciences, and Programs in Occupational Therapy and Physical Therapy, Washington University School of Medicine, St. Louis, Missouri, USA.

6) Kevin J. Black, M.D., Departments of Psychiatry, Neurology, Radiology, and Anatomy \& Neurobiology, and Division of Biology and Biomedical Sciences, Washington University School of Medicine, St. Louis, Missouri, USA.  \href{http://orcid.org/0000-0002-6921-9567}{ORCID 0000-0002-6921-9567}

Address correspondence to Dr. Black at Campus Box 8134, 660 S. Euclid Ave., St. Louis, Missouri, USA, or kevin@WUSTL.edu.

Copyright \copyright\, 2015, the authors

\textbf{NOTE: This was an early draft of an article whose final published version now appears as:}

Siddiqi SH, Abraham NK, Geiger CL, Karimi M, Perlmutter JS and Black KJ (2016) The Human Experience with Intravenous Levodopa. Front. Pharmacol. 6:307. doi: 10.3389/fphar.2015.00307}

  