\section{Results}
139 total articles involving intravenous levodopa administration were reviewed.  Most subjects with parkinsonism were diagnosed with idiopathic PD, while some studies included parkinsonism with a variety of etiologies varying from postencephalitic to vascular.  PD patients differed in their history of prior drug treatment before the studies with conditions including de novo, fluctuating, on-off, and stable.  Some subjects were treated with levodopa for conditions other than PD (see Table 1: Patient Populations and Response Parameters), including other movement disorders (dystonia, progressive supranuclear palsy), primary psychiatric disorders (schizophrenia, mood disorders, personality disorders),  endocrine disorders (diabetes mellitus, essential obesity, hypopituitarism), hepatic disease (alcoholic cirrhosis, steatohepatitis, hepatic encephalopathy), cardiac valvular disease, asthma, and neuroleptic malignant syndrome (NMS).  Normal healthy controls were also used for comparison to investigate safety of the drug.

Pharmacokinetic data were reported for a total of 251 human subjects (see Table 2: Pharmacokinetics of IV Levodopa).  Co-administration of a peripheral decarboxylase inhibitor (PDI) lowered the clearance and elimination half-life of intravenously administered levodopa, while there was no notable effect of PDIs on volume of distribution.
The pharmacodynamic data (see Table 3: Reports of Human Experience with IV Levodopa) obtained from the literature  surveyed a total of 2651 human subjects, with a significant variety of patient groups studied and a multitude of response parameters (see Table 1).  From these articles, no side effects were reported for a total of 1260 subjects.  The highest total dose was 4320 mg in one day, given to a patient with idiopathic PD and carcinoma of the retina.  The patient reported no side effects or adverse effects at this dose.  The highest single bolus dose was 200 mg, while the highest infusion rates were 5.0 mg/kg/hr.

The peripheral decarboxylase inhibitors that were co-administered included carbidopa, benserazide, domperidone, and several investigational agents (Ro-4/2637 and Ro 4-4602).  Often, PDIs affected clearance and volume of distribution (as mentioned above), minimized gastrointestinal symptoms, and allowed subjects to be given lower doses of levodopa.    
Concomitant drugs were also listed to help explain any side effects that might be caused by concomitant drug administration rather than by levodopa alone.  These included istradefylline (adenosine A2A receptor antagonist), amphetamines, methylphenidate, aminophylline, caffeine terguride, estradiol, SKF38393 (a selective D-1 agonist), paroxetine, apomorphine, dextromethorphan, MAO inhibitors, and dantrolene.  

A variety of neurological, psychiatric, cardiovascular, and other physiological effects of levodopa  were monitored in the literature (see Table 1): electroencephalography, electrocardiography, rectal temperature, cerebral perfusion, metabolism, arterial blood pressure, autonomic function, psychosis, mood/anxiety ratings, human growth hormone levels, motor fluctuations, dyskinesias, motor UPDRS (Unified Parkinson’s Disease Rating Scale) scores, tapping rates, walking speed, local cerebral blood flow, heart rate, cardiovascular parameters, AVP (plasma arginine vasopressin), systolic and diastolic blood pressure, pulse, onset of REM and length of REM sleep stage, PR interval, PRA (plasma renin activity), arousal, concentration, digestion, liver and renal function, complete blood counts, and basic metabolic panels.

There were no reported cases of death.  There were no instances of psychosis, even when attempting to elicit it in susceptible subjects (Goetz et al., 1998).  There were also no life-threatening events (serious adverse effects) following intravenous levodopa administration at high doses, regardless of whether a PDI was co-administered.  With co-administration of a PDI, the dosage range causing side effects (mainly nausea and asymptomatic hypotension) was a 0.5-2.0 mg/kg/hr infusion or a 45-150 mg bolus.  Without a co-administered PDI, side effects were reported at a 1.5-3.0 mg/kg/hr infusion or a 60-200 mg bolus. It should be noted that occurrence of side effects was more likely with higher doses, but other factors such as age, gender, and prior treatment also played a role in side effects of levodopa.  

Other than these most common side effects found at high doses, milder, infrequent side effects that were reported included somnolence, lightheadedness, dizziness, headache, disorientation, euphoria, worsening or improvement of tics (in people with Tourette’s syndrome), weakness of the legs, increased dyskinesias and stiffness, REM sleep delay or shortening, improvement of asthma, increased blood pressure, tachycardia, higher cardiac output, benign premature ventricular contractions, urinary urgency, increased renal plasma flow, increase or decrease in plasma renin activity, increased sodium excretion, coldness of the limbs, syncope, “unpleasant sensation in head and abdomen,” reduction or increase in systolic blood pressure, heat sensation, vertigo, dystonia, chorea, emotional fluctuations and elevation in mood ratings, asthenia, insomnia, anxiety, increased "tensori", restlessness, disorientation and confusion, mild sedation, “slight and transient” orthostasis, “mild and transient” increase of PR interval, tachycardia, sweating, mild irritability, and stomachaches.  It is important to note that both side effects and efficacy depended strongly on subject factors including gender, age, past treatment, and disease state.  Also, dsykinesia was mentioned as a side effect only in patients with PD, and most often in those with a long history of previous levodopa treatment.

Motor benefits of levodopa have been demonstrated numerous times. Additional benefits of intravenous levodopa treatment, noted in Table B. included “striking and rapid improvement of the comatose state” (Abramsky, Goldschmidt, 1974); improvement of motor UPDRS scores, including tapping rates (for both sides of the body), walking steps, and walking time; improved sleep (Hardie et al., 1984); improvement of depression and “physical symptoms” (Ingvarsson et al., 1965); reduction of motor symptoms; and attenuation of early morning akinesia or dystonia (Juncos et al., 1987).  It was also mentioned for one subject that dystonia was "abolished" and tapping rate was normalized after two doses of levodopa and a night's sleep (Nutt, Nygaard, 2001).  Several studies have found it to be superior to alternative options for neuroleptic malignant syndrome (Nisijima et al., 1997).  More recently, intravenous levodopa treatment was found to alleviate the neuropsychiatric adverse effects (lethargy, hypersomnia, depression, agitation, akathisia, and confusion) associated with interferon-alpha (Sunami et al., 2002).